Reproducible research in archaeology using R & rrtools

### 2018-03-09 analysis/paper/paper.Rmd
update slides, drop 'advanced repro', move ackno to front

In this presentation we will talk about how archaeologists are changing their data analysis practices to make their research more reproducible and open. We will introduce the rrtools package, which is our specific contribution to help with the challenge of making reproducible research in archaeology easier. "Our" meaning in this case a group of people whose names you can see here and / or who took part in thethe 2017 Summer School on Reproducible Research in Landscape Archaeology at the Freie Universität Berlin (17-21 July), funded and jointly organized by Excellence Cluster 264 Topoi, the Collaborative Research Center 1266, and ISAAKiel under the guidance of Ben Marwick.

## Slide: Motivation

@@

## Slide: Outline

@@

@@

# Acknowledgements

The rrtools project was developed during the 2017 Summer School on Reproducible Research in Landscape Archaeology at the Freie Universität Berlin (17-21 July), funded and jointly organized by Exc264 Topoi, CRC1266, and ISAAKiel.

Thanks to Daniel Knitter, Patrick Kennedy, Nils Müller-Scheeßel, Martin Hinz, Clemens Schmid, Ricarda Braun, Wojciech Francuzik for their contributions to the package.

>>>>

In this presentation we will talk about how archaeologists are changing their data analysis practices to make their research more reproducible and open. We will introduce the rrtools package, which is our specific contribution to help with the challenge of making reproducible research in archaeology easier.

## Acknowledgements

OUr project comes from the group who took part in the 2017 Summer School on Reproducible Research in Landscape Archaeology at the Freie Universität Berlin (17-21 July), funded and jointly organized by Excellence Cluster 264 Topoi, the Collaborative Research Center 1266, and ISAAKiel.

## Slide: Motivation & Outline

 _Motivation_

@@

_Outline_

@@

We have some more advanced functions that we will discuss more at another time.

@@

---

<!--

These are spare slides that might help with Q&A, but not for the main talk

-->
